Let's talk about Thurstone & Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2024-12-07 index.qmd
section:issues,CaseV; process:write

![The effect of different dispersions between stimuli on the distribution of the discriminal difference](/images/figures/dispersion.png){#fig-dispersion width=70%}

@@

![The effect of correlation on the distribution of the discriminal difference](/images/figures/correlation.png){#fig-correlation width=70%}

>>>>

![Discrepancies in the stimuli dispersions and tehir effect on the distribution of the discriminal difference](/images/figures/dispersion.png){#fig-dispersion width=70%}

@@

![The correlation between stimuli and its effect on the distribution of the discriminal difference](/images/figures/correlation.png){#fig-correlation width=70%}
